\bf Visual diagnostics for constrained optimisation with application to guided tours

### 2020-11-17 paper/paper.Rmd
Minor typos

To define projection pursuit, we first need to establish the notation used. Let $\mathbf{X}_{n \times p}$ be the data matrix, with $n$ observations in $p$ dimensions. A d-dimensional projection can be seen as a linear transformation from $\mathbb{R}^p$ into $\mathbb{R}^d$, and defined as $\mathbf{Y} = \mathbf{X} \cdot \mathbf{A}$, where $\mathbf{Y}_{n \times d}$ is the projected data and $\mathbf{A}_{p\times d}$ is the projection matrix. Define $f: \mathbb{R}^{n \times d} \mapsto \mathbb{R}$ to be an index function that maps the projected data $\mathbf{Y}$ (corresponding to an associated projection matrix $\mathbf{A}$) onto an index value $I$. This is commonly known as the projection pursuit index function, or just index function, and is used to measure the "interestingness" of a projection.

@@

The optimisation problem is stated as follows. Given a randomly generated starting basis $\mathbf{A}_1$, projection pursuit finds the final projection basis $\mathbf{A}_T$ that satisfies the following optimisation problem:

>>>>

To define projection pursuit, we first need to establish the notation used. Let $\mathbf{X}_{n \times p}$ be the data matrix, with $n$ observations in $p$ dimensions. A d-dimensional projection can be seen as a linear transformation from $\mathbb{R}^p$ into $\mathbb{R}^d$, and defined as $\mathbf{Y} = \mathbf{X} \cdot \mathbf{A}$, where $\mathbf{Y}_{n \times d}$ is the projected data and $\mathbf{A}_{p\times d}$ is the projection matrix. Define $f: \mathbb{R}^{n \times d} \mapsto \mathbb{R}$ to be an index function that maps the projected data $\mathbf{Y}$ (corresponding to an associated projection matrix $\mathbf{A}$) onto an index value $I$ (QUESTION: Isn't f the index function?). This is commonly known as the projection pursuit index function, or just index function, and is used to measure the "interestingness" of a given projection.

@@

The optimisation problem in the tour context is stated as follows:
....
.Given a randomly generated starting basis $\mathbf{A}_1$, projection pursuit finds the final projection basis $\mathbf{A}_T$ that satisfies the following optimisation problem:

### 2020-11-17 paper/paper.tex
Minor typos

To define projection pursuit, we first need to establish the notation used. Let \(\mathbf{X}_{n \times p}\) be the data matrix, with \(n\) observations in \(p\) dimensions. A d-dimensional projection can be seen as a linear transformation from \(\mathbb{R}^p\) into \(\mathbb{R}^d\), and defined as \(\mathbf{Y} = \mathbf{X} \cdot \mathbf{A}\), where \(\mathbf{Y}_{n \times d}\) is the projected data and \(\mathbf{A}_{p\times d}\) is the projection matrix. Define \(f: \mathbb{R}^{n \times d} \mapsto \mathbb{R}\) to be an index function that maps the projected data \(\mathbf{Y}\) (corresponding to an associated projection matrix \(\mathbf{A}\)) onto an index value \(I\). This is commonly known as the projection pursuit index function, or just index function, and is used to measure the ``interestingness'' of a projection.

@@

The optimisation problem is stated as follows. Given a randomly generated starting basis \(\mathbf{A}_1\), projection pursuit finds the final projection basis \(\mathbf{A}_T\) that satisfies the following optimisation problem:

>>>>

To define projection pursuit, we first need to establish the notation used. Let \(\mathbf{X}_{n \times p}\) be the data matrix, with \(n\) observations in \(p\) dimensions. A d-dimensional projection can be seen as a linear transformation from \(\mathbb{R}^p\) into \(\mathbb{R}^d\), and defined as \(\mathbf{Y} = \mathbf{X} \cdot \mathbf{A}\), where \(\mathbf{Y}_{n \times d}\) is the projected data and \(\mathbf{A}_{p\times d}\) is the projection matrix. Define \(f: \mathbb{R}^{n \times d} \mapsto \mathbb{R}\) to be an index function that maps the projected data \(\mathbf{Y}\) (corresponding to an associated projection matrix \(\mathbf{A}\)) onto an index value \(I\) (QUESTION: Isn't f the index function?). This is commonly known as the projection pursuit index function, or just index function, and is used to measure the ``interestingness'' of a given projection.

@@

The optimisation problem in the tour context is stated as follows:
\ldots.
.Given a randomly generated starting basis \(\mathbf{A}_1\), projection pursuit finds the final projection basis \(\mathbf{A}_T\) that satisfies the following optimisation problem:
